Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach

### 2018-12-08 Manuscript.Rmd
Ok improvements to thresholding

@@

### *Thresholding*
``` {r Threshold this stupid stuff}
# This function will select a two-tailed fiedler vector threshold with respect to the stability of the vertex
# The threshold will be based on proportion DMN given by thresholdRange
threshFV <- function(Data, thresholdRange = c(0.01, 0.99), nthresh = 50) {

  # Iterate over the possible FV until DMN affiliations go below 1%
  count <- 1
  while (meanProp > thresholdRange[1]) {

    # if a threshold meets requirement, store its value
    if (meanProp <= thresholdRange[1]) {
      thresholds[1] <- thresh[count]
    }
    print(count)
    print(meanProp)
    print(thresh[count])
    count <- count + 1

  # Iterate over the possible FV until DMN affiliations go over 99%
  count <- 1
  while (meanProp < thresholdRange[2]) {

}
```
### *Pattern stability over time*

>>>>

# This function will select a two-tailed fiedler vector threshold with respect to the stability of the vertex
# The threshold will be based on proportion DMN given by thresholdRange
threshFV <- function(Data, thresholdRange = c(0.01, 0.99), nthresh = 50) {

  # Iterate over the possible FV until DMN affiliations go below 1%
  count <- 1
  while (meanProp >= thresholdRange[1]) {

    # if a threshold meets requirement, store its value
    if (meanProp <= thresholdRange[1]) {
      thresholds[1] <- thresh[count]
    }

  # Iterate over the possible FV until DMN affiliations go over 99%
  count <- 1
  while (meanProp <= thresholdRange[2]) {

}
```

@@

### *Thresholding*
``` {r Threshold this stupid stuff}
# Get a FV threshold for each subject based on mean vertex stability
# Run the function safely, because some noisy subjects have no relationship between stability and FV
# Note, the mean resulting threshold is similar to the group's 25th and 75th quantiles
TFV <- safely(threshFV)
tempList <- lapply(Summaries, TFV)

# Store thre FV thresholds for all subject 
threshDF <- data_frame(SubjID = substring(subjList,1,6),
                       Lower = NA,
                       Upper = NA)
for (i in seq_along(tempList)) {
  if (is.null(tempList[[i]]$result)) {
    threshDF[i,2:3] <- c(0,0)
  } else {
    threshDF[i,2] <- tempList[[i]]$result[1]
    threshDF[i,3] <- tempList[[i]]$result[2]
  }
}
```
### *Pattern stability over time*
